LSOA domestic Electricty and Gas maps

### 2021-09-02 LSOA domestic Elec and Gas.Rmd
Plotting Change in dom elec against IMD

lsoa_sf_de20102019$pc_diff <- 100*(lsoa_sf_de20102019$de_diff/lsoa_sf_de20102019$de2010)
t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Name.y`,
                         de2010, de2019, de_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
  geom_histogram()
```
####Map with Overlay 
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)

>>>>

lsoa_sf_de20102019$pc_diff <- 100*(lsoa_sf_de20102019$de_diff/lsoa_sf_de20102019$de2010)
t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Name.y`,
                         de2010, de2019, de_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
  geom_histogram()
```
####Plotting the change in dom elec consumption against the deprevation score
```{r Loading in the Deprevation score data}
inFile<-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
LSOAdep<-readr::read_csv(inFile)
LSOAdep$'LSOA11CD' <- LSOAdep$'lsoa11cd'
head(LSOAdep)
names(LSOAdep)
```
```{r plotting change in elec usage against dep}
LSOAdepelec <- merge(merged_de, LSOAdep, by= "LSOA11CD")
names(LSOAdepelec)
df <- dplyr::select(LSOAdepelec, LSOA11CD, "Local Authority Name.x", "de_diff", IMDScore, de2010, IMD_Decile
)

head(df)
Solent <- dplyr::filter(df, `Local Authority Name.x` == "Basingstoke and Deane"|
                           `Local Authority Name.x` == "East Hampshire"|
                           `Local Authority Name.x` == "Eastleigh"|
                           `Local Authority Name.x` == "Fareham"|
                           `Local Authority Name.x` == "Gosport"|
                           `Local Authority Name.x` == "Hart"|
                           `Local Authority Name.x` == "Havant"|
                           `Local Authority Name.x` == "New Forest"|
                           `Local Authority Name.x` == "Portsmouth"|
                           `Local Authority Name.x` == "Rushmoor"|
                           `Local Authority Name.x` == "Southampton"|
                           `Local Authority Name.x` == "Test Valley"|
                           `Local Authority Name.x` == "Winchester"|
                           `Local Authority Name.x` == "Isle of Wight"
                           )

ggplot(Solent,aes(x =as.factor(IMD_Decile)), y =(de_diff/de2010), colour =as.factor(IMD_Decile), group =IMD_Decile) +  geom_boxplot()

nrow(Solent)
```

####Map with Overlay 
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)
